Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-01-19 AO_bondedSi.tex
add new figures from IPython notebooks- VG03, etc.

%\documentclass[osajnl,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1} %% use 11pt for Applied Optics
\documentclass[osajnl,preprint,showpacs,superscriptaddress,12pt]{revtex4-1} %% use 12pt for preprint option
\usepackage{amsmath,amssymb,graphicx}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{longtable}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.95\columnwidth]{figs/fpAbsorbfig}}
\caption{Ratio of transmission of a 0.5 mm thick Si wafer to that of a 3.0 mm thick Si puck.  \label{figSiAbsorbfig} We detect Si absorption shortward of $\lambda \; =$ 1250 nm.  We assume spectral regions longward of 1250 nm are non-absorptive.  The correlated and heteroscedastic measurement errors are typically less than 0.2\%.}
\end{figure}

@@

%The following 3 figures were made with fabry_perot_Si_20140421.pro and other variants.
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/20140421_absolute.pdf}}
\caption{Modeled absolute transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figAbsoluteTrans}.  The absolute transmission through Si depends on wavelength since the refractive index depends minutely on wavelength.  This curve is only accurate for normal incidence transmission.  Furthermore, the curve assumes the multiple reflections within the Si substrates add incoherently as discussed in detail in Appendix \ref{sec:Append-IMRTMM}.}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/Rel_etalon_trans_stack.pdf}}
\caption{Modeled etalon transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 60 nm (cyan triple-dot dashed curve)\label{figEtalonRelTrans}.  The curves are examples from a family defined in Equation \ref{eqFP}.   The limit of no gap is 100\% transmissive, compared to a DSP reference.  A 60 nm gap degrades the transmission over a DSP reference by 12\% at 1200 nm. Modeled etalon transmission through a silicon substrate with gaps of axial extent 35 nm (red dotted curve), 350 nm (green dash-dot curve), and 3500 nm (blue long-dashed curve).  The curves are examples from a family defined in Equation \ref{eqFP}.  The 3500 nm gap curve has obvious Fabry-P\`erot fringes, whereas the 35 and 350 nm gap curves vary smoothly with wavelength.}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=1.0\columnwidth]{figs/VS20fineGapCrop.pdf}}
\caption{Veeco optical profiler surface plot and histogram for part VS20 in the fine pattern section\label{figVS20pattern}.  The four inch diameter VS20 is comprised of two thick silicon wafers.  We patterned three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  The depth was 95 $\pm$ 5 nm as indicated by the well-separated peaks in the Veeco profilometry histogram.  The Veeco was operated in PSI mode.  The purpose for these patterns was to have gaps of known dimensions against which we could test the optical metrology technique we describe in this paper.  The technique can reveal the axial extent and fill factor of an embedded gap.  }
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=.8\columnwidth]{figs/20130911_VS21posM1.pdf}}
\caption{IR transmission spectrum of VS21 (M1) showing consistent gap\label{VS21specm1}.  Example spectrum through part VS21 at a position through the mesh gap of known dimensions.}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=.8\columnwidth]{figs/20130911_VS21posF1}}
\caption{IR transmission spectrum of part VS21 (F1) showing evidence for an excess gap\label{VS21specf1}.  The spectrum was taken at a position through a mesh gap of depth 95 $\pm$5 with 50\% fill factor.  The predicted spectrum lines up with the measurement to within the measurement and model uncertainties.}
\end{figure}

>>>>

%\documentclass[osajnl,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1} %% use 11pt for Applied Optics
\documentclass[osajnl,preprint,showpacs,superscriptaddress,12pt]{revtex4-1} %% use 12pt for preprint option
\usepackage{amsmath,amssymb,graphicx}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{longtable}
\usepackage{subcaption}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.95\columnwidth]{figs/fpAbsorbfig_alt}}
\caption{Ratio of transmission of a 0.5 mm thick Si wafer to that of a 3.0 mm thick Si puck.  \label{figSiAbsorbfig} We detect Si absorption shortward of $\lambda$ = 1250 nm.  The individual measurements have correlated uncertainties attributable to lamp drift at the level of 0.2\%.  The random uncertainties are typically about 0.02\% per sample, though some wavelength regions (e.g. 1700-1900 nm) demonstrate much greater per sample uncertainties.  Absorption longward of 1250 nm (vertical dashed line) is negligible.}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/etalon_trans.pdf}}
\caption{\label{figAbsoluteTrans}The family of curves for transmission as a function of wavelength for various gap sizes in bonded Si optics.  \emph{Top panel}: Absolute transmission through a Si substrate with no gap (top denim-blue solid curve), and small gaps of axial extent 20 nm (green dashed curve), 35 nm (red dash-dotted curve), and 60 nm (purple dotted curve).  The absolute transmission through Si depends on wavelength since the refractive index depends minutely on wavelength.  This curve is only accurate for normal incidence transmission.  Furthermore, the curve assumes the multiple reflections within the Si substrates add incoherently as discussed in detail in Appendix \ref{sec:Append-IMRTMM}.  \emph{Middle panel}: The ``Gap Transmission'', defined as the Absolute transmission through a sample normalized by the absolute transmission through a gapless sample. The gap sizes and colors are the same as in the top panel.  \emph{Bottom panel}: ``Gap Transmission'' for larger gaps, spanning 0-3500 nm.  The 3500 nm sized gap (cyan solid line), demonstrates characteristic Fabry-P\`erot etalon fringes.}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=1.0\columnwidth]{figs/VS20fineGapCrop.pdf}}
\caption{
\label{figVS20pattern}
Veeco optical profiler surface plot and histogram for part VS20 in the fine pattern section.  The 100 mm diameter VS20 is comprised of two thick silicon wafers.  We patterned three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  The depth was 95 $\pm$ 5 nm as indicated by the well-separated peaks in the Veeco profilometry histogram.  The fill factor for this and all mesh patterns was 50\%.  The purpose for these patterns was to have gaps of known axial extent against which we could test the optical metrology technique we describe in this article.}
\end{figure}

@@

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
              \includegraphics[width=\textwidth]{figs/VG03_corner.pdf}
              \caption{Corner plot of our fitted gap size $d$ and fill factor $f$ for VG03}
		\label{figVG03_f100}
        \end{subfigure}

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{figs/VG03_f100.pdf}
                \caption{Measured spectrum and model fit of VG03}
                \label{figVG03_corner}
        \end{subfigure}
        \caption{Pictures of animals}\label{fig:animals}
\caption{

\emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian Process covariance model.

\emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. VG03 has a gap of axial extent $\sim4\;\mu$m implanted in its interface.  The measured spectrum (black stepped line) in this region shows characteristic Fabry-P\`erot fringes of constructive and destructive interference.  The only tunable parameters of the model are the gap axial extent, $d$ and fill factor $f$.  No scaling has been applied.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model, described in the text.  Wavelengths shortward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.
}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth]{gull}
                \caption{A gull}
                \label{fig:gull}
        \end{subfigure}%
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth]{tiger}
                \caption{A tiger}
                \label{fig:tiger}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth]{mouse}
                \caption{A mouse}
                \label{fig:mouse}
        \end{subfigure}
        \caption{Pictures of animals}\label{fig:animals}
\end{figure}
